A publicly available multi-observatory data set of an enhanced network patch from the Photosphere to Corona

### 2021-12-23 Paper1.tex
update Dec 23 2021

\documentclass[twocolumn]{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\newcommand{\figref}[1]{Figure \ref{#1}}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2018}
\revised{January 7, 2018}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\title{Transient brightenings observed with multiple instruments}
\correspondingauthor{Adam R. Kobelski}
\email{adam.kobelski@mail.wvu.edu}

@@

\author[0000-0002-8259-8303]{Lucas A. Tarr}
\affiliation{National Solar Observatory}
%\email{ltarr@nso.edu}
\author[0000-0001-5459-2628]{Sarah Jaeggli}
\affiliation{National Solar Observatory}
%\email{sjaeggli@nso.edu}
\author{Nicholas Luber}
\affiliation{West Virginia University}
%% The \author command can take an optional ORCID.
\author[0000-0001-6102-6851]{Harry P. Warren}
\affiliation{Naval Research Laboratory}
%\email{harry.warren@nrl.navy.mil}
\author[0000-0002-6172-0517]{Sabrina Savage}
\affiliation{NASA Marshall Space Flight Center}
%\email{sabrina.savage@nasa.gov}

\begin{abstract}
%Transient brightenings (TBs) are ubiquitous features of the solar atmosphere across many length and energy scales, the most energetic of which manifest as large-class solar flares. TBs typically originate in regions of enhanced magnetic flux and are observed as increased emission across wavelengths from X-ray to radio, with notable dynamics on timescales of seconds to hours. Coronal TBs are often studied using Extreme Ultravioliet (EUV) and X-ray imaging and spectra. TBs likely originate from photospheric activity such as flux emergence, but are proximately driven by energy transfer through the chromosphere, either by convective waves, direct ejection of chromospheric material, or reconnection. Chromospheric and transition region observations of these events have only become routine in the last decade. 
%Chromospheric and transition region observations of these events have not been routine for the last few decades. 
New instruments sensitive to chromospheric radiation at X-ray, UV, Visible, IR, and sub-mm wavelengths have become available that significantly enhance our ability to understand the bi-directional flow of energy through the chromosphere. In this paper, we showcase and combine a new dataset utilizing a large number of these instruments to obtain multi-wavelength chromospheric observations capable of improving our understanding of the connectivity between the photosphere and the corona in the chromosphere via transient brightenings and wave signatures. This comprehensive study provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date. SOME NUMBERS, SCIENCE CONCLUSIONS.

\end{abstract}
\keywords{The Sun, Radio, X-Ray, EUV}

\section{Introduction} \label{sec:intro}
The methods of transporting energy from the photosphere through the chromosphere to the million degree corona have been debated since the discovery of the hot corona \citep[][]{1933LyotMarshall, 1939Grotrian}. 
The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the corona to the chromosphere, so the energy in the corona must constantly be resupplied.  
One of the early ideas for this transport of energy was via wave activity through hydrodynamic shocks \citep[][]{1949Schatzman} and later, once the central role of magnetic fields on the Sun was fully realized, by magnetoacoustic or Alfv\'en waves \citep{1961Osterbrock}. 
In this scenario, convective energy drives the waves which carry energy as they propagate upward through to the corona, and eventually deposit that energy as they cascade to small length-scales and heat the plasma through dissipation \citep{2014vanBallegooijenEA_FootpointMotion}.

@@

As an alternative to wave heating, it has been posited that small-scale magnetic reconnection via nanoflares \citep[][]{1983Parker} could be responsible for the heating of the corona. 
It was thought that these nanoflares would manifest themselves as small scale brightenings in the corona, sometimes referred to as microflares or active region transient brightenings \citep[][]{1984LinEA_microflares, 1991Hudson, 1992ShimizuEA, 1995Shimizu}. 
\citet{1997GaryEA} determined that the small scale-brightenings exhibit the same signatures of particle acceleration as larger solar flares and concluded that many of the transient brightenings (TBs) were also products of magnetic reconnection. \latcomment{Reference some of the NuSTAR or Foxi work about this?} 
A key suggestion of the Parker nanoflare model was that the reconnection would occur due to substructure in the magnetic field lines, in which the observed loops consist of many unresolved braided magnetic strands. 
The concept of unresolved strands is in agreement with forward models of the observations \citep[e.g.][]{2012BrooksEA, 2014KobelskiEA_XRTTBs, 2014KobelskiMcKenzie_HiC}, and has been strongly suggested by direct observation in extreme ultraviolet (EUV) with the Hi-C sounding rocket \citep[][]{2013CirtainEA_HiC}.

@@

In this paper, we present a unique, robust, and extensive data set with which to study the flow of energy through the chromosphere and the interplay between transients and wave activity. 
Even though the data set is of a quiescent solar region, it displays notable dynamics from the photosphere to the corona. 
This region is exemplary of the ubiquitous features found throughout the solar atmosphere during all phases of the solar cycle. 
The type of analysis we propose has been performed for active regions and strong plage, \emph{but not quiescent regions}. 
Since this data set probes each layer of the Sun in multiple wavelengths, heights, temperatures, and methodologies, it can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.

The data set includes photospheric magnetic field information from the Helioseismic and Magnetic Imager \citep[HMI,][]{2012SchouEA_HMI} as well as imaging from the Atmospheric Imaging Assembly \citep[AIA,][]{2012LemenEA_AIA} on board the Solar Dynamics Observatory \citep[SDO,][]{2012PesnellEA_SDO}; photospheric magnetic field data from the Solar Optical Telescope \citep[SOT,][]{2008TsunetaEA_SOT}, coronal X-ray imaging from the X-Ray Telescope \citep[XRT,][]{2007GolubEA_XRT}, and EUV spectra from EIS \citep{2007CulhaneEA_EIS} on board the {\it Hinode} spacecraft \citep[][]{2007KosugiEA_Hinode}; chromospheric images and spectra from IRIS \citep{2014DePontieuEA_IRIS}; spectral images from the  Interferometric BIdimensional Spectropolarimeter \citep[IBIS,][]{2006Cavallini_IBIS} and infrared spectropolarimetry from the Facility InfraRed Spectropolarimeter \citep[FIRS,][]{2010JaeggliEA_FIRS} at the Dunn Solar Telescope (DST); and millimeter wave information from the Atacama Large Millimeter Array \citep[ALMA,][]{2009WootenThompson_ALMA, 2010HillsEA_ALMA2}.

In this paper, we describe the reduction of the imaging and spectral observations, as well as the co-alignment between instruments. 
We then interpret and compare activity between atmospheric layers, though a more thorough analysis is forthcoming.  
We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign} and their analysis in Section~\ref{sec:analysis}, with concluding remarks in \ref{sec:conclusion}.

\section{Data} \label{sec:data}
\subsection{Overview and Coordination}
The data sets presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations. Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.  
Given these constraints, the coverage is, in general, fairly good.

\figref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window.
Fortuitously, NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}.
The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/obs_timing}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs.png}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs_zoom.png}
    \caption{Overview of all observations around the ALMA observing window.  Upper plot: timing information, where instruments are ordered vertically roughly according to height in the solar atmosphere.  Gaps in each color band indicate data gaps in that data channel.  Lower panels: approximate FOVs for each instrument using the same colors as in the upper panel, overlaid on an SDO/AIA-193\AA{} context image.}
    \label{fig:coordination}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/IBISimg0108.eps}
    \caption{Representative sample of co-aligned images. The SOT data has been rotated to align with the coordinate time of the IBIS data. The ALMA data ranges from $\pm$some number of K}
    \label{fig:coordination}
\end{figure}

\subsection{SDO/AIA}\label{sec:sdoaia}
AIA obtains full-disk images of the Sun every 12 seconds with 0.6\arcsec{} spatial sampling in a variety of visible, UV, EUV channels.
Observations from all AIA channels are available throughout the entire coordination period.
The Level 1 AIA data was downloaded from the Joint Science Operations Center (JSOC)\footnote{\url{http://jsoc.stanford.edu/}}, updated to Level 1.5 using \fnc{aia\_prep.pro} as described in the SDO Analysis Guide.
We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other datasets (14:00-17:00 UT on 2017-03-21).
The 193 \AA\ channel of AIA was primarily used for co-alignment and to provide full-disk context for the other observations.  
The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively.

\subsection{SDO/HMI}
We used three days of intensity and line-of-site (LOS) magnetograms from the level 1.5 \texttt{hmi.M\_720s} and \texttt{hmi.Ic\_720s} series\footnote{JSOC query: \texttt{hmi.M\_720s[2017.03.19\_00:00:00\_TAI/3d]}, and similar for intensity.}.  
An area $\approx330\arcsec{}\times250\arcsec{}$ was tracked using solar rotation to understand the magnetic evolution of the region leading up to and throughout the coordinated observations.  
To ease later analysis, we derotated all HMI data so that the solar North-South axis aligned with columns of the data array, with North pointing upward, but kept the spatial scaling of the original HMI data.  
The typical extra step of spatially-rescaling the data to match AIA  has little benefit for use given that our various datasets include many different spatial samplings.

\subsection{ALMA}
\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz \citep{2009WootenThompson_ALMA}. ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. These 66 dishes are arranged as such to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance. The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky. Our integration time is 2 seconds, and the entire observation, including the target field and calibrators, had a duration of 1.03 hours.

\paragraph{ALMA calibration} The ALMA Band 3 data were cross-calibrated using the standard ALMA pipeline Cycle 4 version\footnote{For a thorough description of the tasks and philosophy see: ALMA Pipeline Team, 2017, ALMA Science Pipeline User’s Guide, ALMA Doc 4.13v2.0}. in CASA version 4.7.2 \citep{casa}. The observations were taken with the strong millimeter source, J2253+1608, approximately 6.5 Jy in ALMA Band 3, used for the bandpass and flux calibration, and the strong millimeter source, QSO\_B0003-066, approximately 2 Jy in ALMA Band 3, used for the phase cross calibration. The initial cross-calibration eliminated 4 dishes due to unreasonably elevated system temperatures, and produced images of a reasonable quality, but still suffering from some poor calibration artifacts.

\paragraph{ALMA self-calibration} In order to improve the fidelity of our images, we then phase-only self-calibrate the data. The phase-only self-calibration is an iterative process in which we took the following steps. We first produce a cleaned map of the data, but we clean only to a relatively modest level, to ensure all flux captured in the clean model is real. We then do a phase-only gaincal over a large time-range, in the first iteration this was a scan length (5 minutes), using the clean model, and apply this calibration to the data. We do this process iteratively, where in each iteration we clean to a lower flux threshold, and shorten the time-range used in the phase-only self calibration. We terminate the process when there is no decrease in out-of-field r.m.s. noise, and the image shows little-to-no improvement. The improvements caused by this process are the elimination of PSF pattern relics in the image, and the sharpening of the image, which is why this process if often compared to the effect of focusing a telescope or microscope.

\paragraph{ALMA issues with phase-center}

\subsection{DST/IBIS}
IBIS is a dual Fabry-Perot interferometer- (FPI-) based imaging spectropolarimeter that was mounted at the Dunn Solar Telescope.
The FPI cavity is tuned to transmit a narrow bandpass $(\approx 2.4\unit{pm})$, and the tuning is modulated to step the bandpass over the wavelength range of the line.
We used IBIS in spectal-only mode (no polarimetry) with a circular field stop of approximately 90\arcsec{} diameter.
We continuously sampled the \halpha{} line between 14:46-16:55 UT using 26 wavelength positions, with $\approx 12.5\unit{pm}$ spacing near line core and $\approx 19.1\unit{pm}$ spacing in the wings.  
Each narrow band image is paired with a strictly cotemporally acquired broad band continuum image taken in a nearby wavelength band at $660\unit{nm}$.
The broad band image is used for speckle reconstruction, self alignment of the narrow band images, and co-alignment between the IBIS data and other data series, e.g., to the HMI continua data series. \par

>>>>

\documentclass[twocolumn]{aastex62}
\usepackage{amssymb,amsmath,amsopn}
%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\newcommand{\figref}[1]{Figure \ref{#1}}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2022}
\revised{January 7, 2022}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

\title{A publicly available multi-observatory data set of an enhanced network patch from the Photosphere to Corona}
\correspondingauthor{Adam R. Kobelski}
\email{adam.kobelski@nasa.wvu.edu}

@@

\author[0000-0002-8259-8303]{Lucas A. Tarr}
\affiliation{National Solar Observatory}
%\email{ltarr@nso.edu}
\author[0000-0001-5459-2628]{Sarah A. Jaeggli}
\affiliation{National Solar Observatory}
%\email{sjaeggli@nso.edu}
\author{Nicholas Luber}
\affiliation{West Virginia University}
%% The \author command can take an optional ORCID.
\author[0000-0001-6102-6851]{Harry P. Warren}
\affiliation{Naval Research Laboratory}
%\email{harry.warren@nrl.navy.mil}
\author[0000-0002-6172-0517]{Sabrina Savage}
\affiliation{NASA Marshall Space Flight Center}
%\email{sabrina.savage@nasa.gov}

\begin{abstract}
%Transient brightenings (TBs) are ubiquitous features of the solar atmosphere across many length and energy scales, the most energetic of which manifest as large-class solar flares. TBs typically originate in regions of enhanced magnetic flux and are observed as increased emission across wavelengths from X-ray to radio, with notable dynamics on timescales of seconds to hours. Coronal TBs are often studied using Extreme Ultravioliet (EUV) and X-ray imaging and spectra. TBs likely originate from photospheric activity such as flux emergence, but are proximately driven by energy transfer through the chromosphere, either by convective waves, direct ejection of chromospheric material, or reconnection. Chromospheric and transition region observations of these events have only become routine in the last decade. 
%Chromospheric and transition region observations of these events have not been routine for the last few decades. 
New instruments sensitive to chromospheric radiation at X-ray, UV, Visible, IR, and sub-mm wavelengths have become available that significantly enhance our ability to understand the bi-directional flow of energy through the chromosphere.
We describe the calibration, coalignment, initial results, and public release of a new data set combining a large number of these instruments to obtain multi-wavelength photospheric, chromospheric, and coronal observations capable of improving our understanding of the connectivity between the photosphere and the corona via transient brightenings and wave signatures.
The observations center on a bipolar region of enhanced network magnetic flux near disk center on SOL2017-03-17T14:00-17:00.
The comprehensive data set provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date.
Our initial analysis shows strong spatial correspondence between the areas of broadest width of the Hydrogen$\alpha$ spectral line and the hottest temperatures observed in ALMA Band 3 radio data.
The correspondence persists for the duration of cotemporal obserations ($\approx 60\unit{m}$).
Numerous transient brightenings were observed in multiple data series.
We highlight a single well observed transient brightening along a set of thin filamentary features with a duration of 20 minutes.
The timing of the peak intensity transitions from the cooler (ALMA, 7000K) to hotter (XRT, 3MK) data series.
\end{abstract}
\keywords{The Sun, Radio, X-Ray, EUV}

\section{Introduction} \label{sec:intro}
The methods of transporting energy from the photosphere through the chromosphere to the million degree corona have been debated since the discovery of the hot corona \citep[][]{1933LyotMarshall, 1939Grotrian}. 
The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the hot corona to the cool chromosphere from which it rapidly radiates away, so the energy in the corona must constantly be resupplied.
One of the early ideas for this transport of energy was via wave activity through hydrodynamic shocks \citep[][]{1949Schatzman} and later, once the central role of magnetic fields on the Sun was fully realized, by magnetoacoustic or Alfv\'en waves \citep{1961Osterbrock}. 
In this scenario, convective energy drives the waves which carry energy as they propagate upward through to the corona, and eventually deposit that energy as they cascade to small length-scales and heat the plasma through dissipation \citep{2014vanBallegooijenEA_FootpointMotion}.

@@

As an alternative to wave heating, it has been posited that small-scale magnetic reconnection via nanoflares \citep[][]{1983Parker} could be responsible for the heating of the corona. 
It was thought that these nanoflares would manifest themselves as small scale brightenings in the corona, sometimes referred to as microflares or active region transient brightenings \citep[][]{1984LinEA_microflares, 1991Hudson, 1992ShimizuEA, 1995Shimizu}. 
\citet{1997GaryEA} determined that the small scale-brightenings exhibit the same signatures of particle acceleration as larger solar flares and concluded that many of the transient brightenings (TBs) were also products of magnetic reconnection. 
The details of this connection could have important ramifications for some coronal heating theories,nand is thust still under active study (as seen by the work of Hannah et al, NuStar and MAGIXs, FOXSI among others).
A key suggestion of the Parker nanoflare model was that the reconnection would occur due to substructure in the magnetic field lines, in which the observed loops consist of many unresolved braided magnetic strands. 
The concept of unresolved strands is in agreement with forward models of the observations \citep[e.g.][]{2012BrooksEA, 2014KobelskiEA_XRTTBs, 2014KobelskiMcKenzie_HiC}, and has been strongly suggested by direct observation in extreme ultraviolet (EUV) with the Hi-C sounding rocket \citep[][]{2013CirtainEA_HiC}.

@@

In this paper, we present a unique, robust, and extensive data set with which to study the flow of energy through the chromosphere and the interplay between transients and wave activity.
Calibrated and coaligned data in FITS format with WCS compliant coordinates are available through a publicly accessible archive hosted at the National Solar Observatory \url{https://share.nso.edu/shared/dkist/ltarr/kolsch/}.
Even though the data set is of a quiescent solar region, it displays notable dynamics from the photosphere to the corona. 
This region is exemplary of the ubiquitous features found throughout the solar atmosphere during all phases of the solar cycle. 
The type of analysis we propose has been performed for active regions and strong plage, \emph{but not quiescent regions}. 
Since this data set probes each layer of the Sun in multiple wavelengths, heights, and temperatures, it can be studied with distinct methodologies, and can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.

The data set includes photospheric magnetic field information from the Helioseismic and Magnetic Imager \citep[HMI,][]{2012SchouEA_HMI} as well as imaging from the Atmospheric Imaging Assembly \citep[AIA,][]{2012LemenEA_AIA} on board the Solar Dynamics Observatory \citep[SDO,][]{2012PesnellEA_SDO}; photospheric magnetic field data from the Solar Optical Telescope \citep[SOT,][]{2008TsunetaEA_SOT}, coronal X-ray imaging from the X-Ray Telescope \citep[XRT,][]{2007GolubEA_XRT}, and EUV spectra from EIS \citep{2007CulhaneEA_EIS} on board the {\it Hinode} spacecraft \citep[][]{2007KosugiEA_Hinode}; chromospheric images and spectra from IRIS \citep{2014DePontieuEA_IRIS}; spectral images from the  Interferometric BIdimensional Spectropolarimeter \citep[IBIS,][]{2006Cavallini_IBIS} and infrared spectropolarimetry from the Facility InfraRed Spectropolarimeter \citep[FIRS,][]{2010JaeggliEA_FIRS} at the Dunn Solar Telescope (DST); and millimeter wave information from the Atacama Large Millimeter Array \citep[ALMA,][]{2009WootenThompson_ALMA, 2010HillsEA_ALMA2}.  For consistency, we refer each individual instrument's collected data as a \emph{data series} and the full collection of data series as the data set.

In this paper, we describe the reduction of the imaging and spectral observations, as well as the co-alignment between instruments. 
We then compare activity between atmospheric layers and provide a preliminary interpretation. 
More thorough analyses are forthcoming. 
We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign}, some preliminary analysis in Section~\ref{sec:analysis}, and concluding remarks in \ref{sec:conclusion}.

\section{Data} \label{sec:data}
\subsection{Overview and Coordination}
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/obs_timing}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs.png}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs_zoom.png}
    \caption{Overview of all observations around the ALMA observing window.  Upper plot: timing information, where instruments are ordered vertically roughly according to height in the solar atmosphere.  Gaps in each color band indicate data gaps in that data channel.  Lower panels: approximate FOVs for each instrument using the same colors as in the upper panel, overlaid on an SDO/AIA-193\AA{} context image.}
    \label{fig:coordination}
\end{figure}
The data series presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations. Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.  
Given these constraints, the coverage is, in general, fairly good.

Figure \ref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window, while SDO and AIA provide near-continuous observations in a variety of wavelengths, as always.
The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.

Figure \ref{fig:coordination2} shows a representative sample of coaligned images from each of the data channels and provides an overview of the target region on the Sun.
The images are approximately co-temporal at 16:27UT and are taken partway though a transient brightening event.
From left to right and top to bottom (and roughly moving from the photosphere through the chromosphere and into the corona) the panels show: 
\begin{itemize}
    {\item (SOT) The photospheric magnetic field including a bipolar region of enhanced network flux}
    {\item (SOT) The solar granulation pattern, including some minor disruptions by the enhanced network concentrations}
    {\item (ALMA) Plasma temperature variations, with hotter/brighter areas roughly coincident with the photospheric magnetic field concentrations}
    {\item (IBIS) \halpha{} blue wing, which shows some dynamic spicules (dark) and the magnetic concentrations (bright)}
    {\item (IBIS) \halpha{} line center, which shows a central sigmoidal filament above the magnetic polarity inversion line}
    {\item (IRIS) Si IV intensity, which shows transient brightenings throughout the FOV, yet mostly concentrated above the enhanced network flux}
    {\item (AIA) 304\AA{} emission, which shows multiple loop brightenings against background of structured emission}
    {\item (AIA) 193\AA{} emission showing multiple loop brightenings}
    {\item (XRT) X-ray emission showing multiple transient strands}
\end{itemize}
We discuss this event in more detail in Section~\ref{sec:analysis} below.
NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}, confirming continued X-ray activity after the end of our primary coordinated observations, although we do not condsider the NuSTAR observations in the current study.
The remaining subsections describe each data series from the coordinated observations.
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/IBISimg0108.eps}
    \caption{Representative sample of co-aligned images. The SOT data has been rotated to align with the coordinate time of the IBIS data. The ALMA data ranges from $\pm$some number of K}
    \label{fig:coordination2}
\end{figure}

\subsection{SDO/AIA}\label{sec:sdoaia}
AIA obtains full-disk images of the Sun every 12 seconds with 0.6\arcsec{} spatial sampling in a variety of visible, UV, EUV channels.
Observations from all AIA channels are available throughout the entire coordination period.
The Level 1 AIA data was downloaded from the Joint Science Operations Center (JSOC)\footnote{\url{http://jsoc.stanford.edu/}}, updated to Level 1.5 using \fnc{aia\_prep.pro} as described in the SDO Analysis Guide.
We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other data series (14:00-17:00 UT on 2017-03-21).
The 193 \AA\ channel of AIA was primarily used for co-alignment and to provide full-disk context for the other observations.  
The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively, as described in \citet{2012Boerner} and \citet{2014Boerner}.

\subsection{SDO/HMI}
We used three days of intensity and line-of-site (LOS) magnetograms from the level 1.5 \texttt{hmi.M\_720s} and \texttt{hmi.Ic\_720s} series\footnote{JSOC query: \texttt{hmi.M\_720s[2017.03.19\_00:00:00\_TAI/3d]}, and similar for intensity.}.  
An area $\approx330\arcsec{}\times250\arcsec{}$ was tracked using solar rotation to understand the magnetic evolution of the region leading up to and throughout the coordinated observations.  
To ease later analysis, we derotated all HMI data so that the solar North-South axis aligned with columns of the data array, with North pointing upward, but kept the spatial scaling of the original HMI data.  
The typical extra step of spatially-rescaling the data to match AIA  has little benefit in the present context given that our various data series include many different spatial samplings.

\subsection{ALMA}
\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz \citep{2009WootenThompson_ALMA}. 
ALMA is constituted of 66 telescope dishes: 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. 
These 66 dishes are arranged to ensure that ALMA has suitable sensitivity to large-scale diffuse emission, achieved by the high density of centrally located dishes, and excellent resolution to small scale features, achieved with the dishes at long distance. 
For this particular observation, ALMA was in its most compact configuration (C43-1), which limits the small scale resolution, but provides the best available resolution on larger scales, and also minimizes issues caused by water vapor in the Earth's atmosphere above the telescope.
The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. 
At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky. 
Our integration time is 2 seconds, and the entire observation, including the target field and calibrators, had a duration of 1.03 hours.
